Paper_stuff

### 2023-09-20 Paper_stuff.Rmd
Pre/Post Scores!!

@@

Main_Treat <- Mothership |>

@@

Pre_Post
```{r}
Mothership_post <- Mothership |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!Days_complete_1 > 40,
         !Days_complete_1 == 0,
         !is.na(BL_CUXOS),
         !is.na(SUManx_DC),
         BL_CUXOS > 1,
         SUManx_DC > 0,
         !is.na(BL_CUDOS),
         !is.na(SUMdep_DC),
         BL_CUDOS > 1,
         SUMdep_DC > 0
         ) |>
  mutate(
    Delta_Anx_DC =  SUManx_DC - BL_CUXOS,
    Delta_Dep_DC = SUMdep_DC - BL_CUDOS,
    Percent_Anx_change = (Delta_Anx_DC/BL_CUXOS)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/BL_CUDOS)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(BL_CUXOS > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(BL_CUXOS > 10 & Percent_Anx_change > 0, "Anx Worse", 
      ifelse(BL_CUXOS > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50,  "Unresponders", "Low BL Anx"      
      )))),
    Dep_Responder = as.factor(
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange > 0, "Dep Worse", 
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50,  "Unresponders", "Low BL Dep" 
      )))),
    Treatment_Responder = as.factor(
      ifelse(BL_CUXOS > 10 & BL_CUXOS > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(BL_CUXOS > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange > 0 & BL_CUXOS > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(BL_CUXOS > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(BL_CUXOS > 10 & BL_CUDOS > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(BL_CUXOS > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

@@

ggplot(Mothership_post, aes(x = Dep_Responder)) +
  geom_bar() +
  coord_flip() +
    labs(
    title = "Treatment response of Depression",
    subtitle = "Response = 50% reduciton in scores if BL score > 10")

mean(Mothership_post$Percent_anx_change)
ggplot(Mothership_post,aes(x = Anx_Responder, y = Percent_Anx_change)) +
         geom_boxplot() +
         ylim(-50,500) + 
  scale_x_discrete(limits = c(
    ""
  ))

#2. Create pre_scores
      # CUXOS_pre = Day1_CUXOS,
      # CUDOS_pre = Day1_CUDOS
      # )

sum(Mothership_post$SUManx_DC < 0)

(40-50)/50
```

>>>>

# only include people that attend treatment & its thier first time attending
Mothership <- Mothership |>
        filter(
          is.na(Prev_AdmitID_1),
          C_Admit_1 == 1
          ) |>
        mutate(
          dummy = -99
        )

@@

@@

Pre_Post
### Extract pre/post scores
```{r}
#1. load DF
    Mothership_post <- Mothership_Diag_treat

    # Depressiopn
    CUDOS_Score_post <-  select(Mothership_post, dummy,Day1_CUDOS:Day40_CUDOS)
    # Anxiety
    CUXOS_Score_post <- select(Mothership_post, dummy,Day1_CUXOS:Day40_CUXOS)

#2. Getting post scores for people who have NA for post

    # Depression
    Post_DEP <- NA
    PD_df <- NA
    for(i in 1:nrow(CUDOS_Score_post)){
    PD_df <- unname(unlist(CUDOS_Score_post[i,]))
    PD_df <- PD_df[!is.na(PD_df)]
    PD_df <- tail(PD_df, n=1)
    Post_DEP <- rbind(Post_DEP,PD_df)
    }
    Post_Dep <- Post_DEP[-1]

    # Anxiety
    Post_ANX <- NA
    PA_df <- NA
    for(i in 1:nrow(CUXOS_Score_post)){
    PA_df <- unname(unlist(CUXOS_Score_post[i,]))
    PA_df <- PA_df[!is.na(PA_df)]
    PA_df <- tail(PA_df, n=1)
    Post_ANX <- rbind(Post_ANX,PA_df)
    }
    Post_anx <- Post_ANX[-1]

# 3. Getting BL scores for people who have NA at Baseline

    # Depression / Anxiety Dummy variable
    CUDOS_Score_pre <-  select(Mothership_post, Day1_CUDOS:Day40_CUDOS,dummy)
    CUXOS_Score_pre <- select(Mothership_post, Day1_CUXOS:Day40_CUXOS,dummy)

    # Depression
    Pre_DEP <- NA
    PD_df <- NA
    for(i in 1:nrow(CUDOS_Score_pre)){
    PD_df <- unname(unlist(CUDOS_Score_pre[i,]))
    PD_df <- PD_df[!is.na(PD_df)]
    PD_df <- head(PD_df, n=1)
    Pre_DEP <- rbind(Pre_DEP,PD_df)
    }
    Pre_dep <- Pre_DEP[-1]

    # Anxiety
    Pre_ANX <- NA
    PA_df <- NA
    for(i in 1:nrow(CUXOS_Score_pre)){
    PA_df <- unname(unlist(CUXOS_Score_pre[i,]))
    PA_df <- PA_df[!is.na(PA_df)]
    PA_df <- head(PA_df, n=1)
    Pre_ANX <- rbind(Pre_ANX,PA_df)
    }
    Pre_anx <- Pre_ANX[-1]

#4 Adding it back to mother ship
    Mothership_post <- Mothership_post |>
      mutate(
        CUDOS_pre = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
          CUDOS_pre = ifelse(CUDOS_pre < 0, NA, CUDOS_pre),
        CUXOS_pre = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
          CUXOS_pre = ifelse(CUXOS_pre < 0, NA, CUXOS_pre),
        CUDOS_post = ifelse(Post_Dep < 0, NA, Post_Dep),
        CUXOS_post = ifelse(Post_anx < 0, NA, Post_anx)
      )

#7. create new DF with Varaibles we want

AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_treat,
                                  Mothership_post$CUDOS_pre,
                                  Mothership_post$CUDOS_post,
                                  Mothership_post$CUXOS_pre,
                                  Mothership_post$CUXOS_post)) %>%
  filter(!is.na(Mothership_post$Disorder_Type))

colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post")

#8. Create long data frame

AnxDep_PrePost_Long <- AnxDep_PrePost %>% 
  pivot_longer(
    cols = CUDOS_pre:CUXOS_post, 
    names_to = "Test",
    values_to = "Score"
  )
AnxDep_PrePost_Long <-AnxDep_PrePost_Long %>%
  mutate(
    PrePost = ifelse(
      Test == "CUDOS_pre", "Pre",
      ifelse(Test == "CUXOS_pre" , "Pre", "Post"
    )),
    Score = as.integer(Score),
    Test = as.factor(Test),
    Test = as.factor(ifelse(Test == "CUDOS_pre",  "CUDOS",
                     ifelse(Test == "CUDOS_post", "CUDOS", "CUXOS"
                     ))))

#9. Convert to data frame with means of values to be plotted
AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
  group_by(Test,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

### Overall Plot
```{r}
# Pre Post CUDOS/CUXOS Plot
ggplot(data=AnxDep_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=Test))+
  geom_point(size=2.5)+
  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())

### Line Plot By Disorder
```{r}
#1. Creaate new datasets with only anxiety / depresssion

ANX_PrePost<- AnxDep_PrePost_Long %>%
  filter(Test == "CUXOS")

DEP_PrePost<- AnxDep_PrePost_Long %>%
  filter(Test == "CUDOS")

#2. Create DF grouped buy disorder type
ANX_PrePost_mean<-ANX_PrePost %>%
  group_by(Disorder_Type,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

DEP_PrePost_mean<-DEP_PrePost %>%
  group_by(Disorder_Type,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

#### ANX
ggplot(data=ANX_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_point(size=2.5)+
  geom_line(size=1)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUXOS Score")+
  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUXOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())

#### DEP
ggplot(data=DEP_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_point(size=2.5)+
  geom_line(size=1)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS Score")+
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self report depression was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())
```

### Dumbell Plot by Disorder
```{r}
Pre_ANX<-ANX_PrePost_mean %>%
  filter(PrePost == "Pre")

Post_ANX<-ANX_PrePost_mean %>%
  filter(PrePost == "Post")

Plot_Text<- dplyr::count(ANX_PrePost, Disorder_Type)
Plot_Text

"#aeb6bf"

ggplot(data=Pre_ANX,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUXOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))

#sum(as.factor(ANX_PrePost$Disorder_Type))

Pre_DEP<-DEP_PrePost_mean %>%
  filter(PrePost == "Pre")

Post_DEP<-DEP_PrePost_mean %>%
  filter(PrePost == "Post")

ggplot(data=Pre_DEP,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
       ylab = "Disorder Type")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))
```

```{r}
Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50,  "Unresponders", "Low BL Anx"      
      )))),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse", 
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50,  "Unresponders", "Low BL Dep" 
      )))),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

@@

ggplot(Mothership_post, aes(x = Dep_Responder)) +
  geom_bar() +
  coord_flip() +
    labs(
    title = "Treatment response of Depression",
    subtitle = "Response = 50% reduciton in scores if BL score > 10")
```
